quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-24 paper-quollr.Rmd
Updated Figure 7 title.

```{r, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="$2\\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

@@

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plots showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `langevitour`.", layout = "l-page"}

@@

```{r, echo=TRUE, fig.cap="Link plots showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`.", eval=knitr::is_html_output(), layout = "l-page"}

@@

@@

```{r, out.width=c("100%", "100%"), fig.cap="Screenshots of the link plots showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`.", fig.pos="H", fig.show='hold', eval=knitr::is_latex_output()}

@@

```{r, echo=TRUE, fig.cap="Link plots showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`.", eval=knitr::is_html_output(), layout = "l-page"}

>>>>

```{r, eval=knitr::is_latex_output(), fig.pos='H', fig.cap="$2\\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (blue) overlaid on `Scurve` data (black) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model."}

@@

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `langevitour`. Brushing in either view highlights the corresponding subset of points across both representations, allowing examination of how well the NLDR layout preserves the underlying `Scurve` structure. Double-clicking on either view clears the selection and dehighlights all points.", layout = "l-page"}

@@

```{r, echo=TRUE}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Interactive link plots showing the link between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`. Brushing in either view highlights the corresponding subset of points across both representations, allowing examination of how well the NLDR layout preserves the underlying `Scurve` structure. To highlight points in `detourr`, use the Select button. Double-clicking on either view clears the selection and dehighlights all points.", layout = "l-page"}

@@

```{r, eval=knitr::is_latex_output(), out.width=c("100%", "100%"), fig.cap="Screenshots of the link plots showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`.", fig.pos="H", fig.show='hold'}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plots showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right) using `detourr`.", layout = "l-page"}

### 2025-10-24 paper-quollr.tex
Updated Figure 7 title.

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-29-1} \caption{$2\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (black) overlaid on `Scurve` data (in purple) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model.}\label{fig:unnamed-chunk-29}
\end{figure}

@@

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "600px", height = "600px")

crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                   nldr_plt,
                   htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
  )
\end{verbatim}

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/model_link_proj1_detourr} \includegraphics[width=1\linewidth]{figures/model_link_proj2_detourr} \caption{Screenshots of the link plots showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\text{-}D$ (right) using `detourr`.}\label{fig:unnamed-chunk-41}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/model_link_error_proj1_detourr} \includegraphics[width=1\linewidth]{figures/model_link_error_proj2_detourr} \caption{Screenshots of the link plots showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\text{-}D$ (right) using `detourr`.}\label{fig:unnamed-chunk-44}
\end{figure}

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{paper-quollr_files/figure-latex/unnamed-chunk-29-1} \caption{$2\text{-}D$ projections of the lifted high-dimensional wireframe model from the `Scurve` UMAP layout. Each panel (a1–a4) shows the model (blue) overlaid on `Scurve` data (black) in different projections. These views illustrate how the lifted wireframe model captures the structure of the `Scurve` data. The two twists visible in the UMAP layout can also be seen in the lifted model.}\label{fig:unnamed-chunk-29}
\end{figure}

@@

\begin{verbatim}
detourr_output <- detour(
  shared_df,
  tour_aes(
    projection = starts_with("x"),
    colour = type
  )
) |>
  tour_path(grand_tour(2), 
                    max_bases=50, fps = 60) |>
  show_scatter(axes = TRUE, size = 1, alpha = 0.8, 
               edges = as.matrix(trimesh[, c("from_reindexed", "to_reindexed")]),
               palette = c("#66B2CC", "#FF7755"),
                width = "600px", height = "600px")
\end{verbatim}

\begin{verbatim}
crosstalk::bscols(
    htmltools::div(style="display: grid; grid-template-columns: 1fr 1fr;",
                   nldr_plt,
                   htmltools::div(style = "margin-top: 20px;", detourr_output)
    ),
    device = "xs"
  )
\end{verbatim}

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/model_link_proj1_detourr} \includegraphics[width=1\linewidth]{figures/model_link_proj2_detourr} \caption{Screenshots of the link plots showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\text{-}D$ (right) using `detourr`.}\label{fig:unnamed-chunk-42}
\end{figure}

@@

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/model_link_error_proj1_detourr} \includegraphics[width=1\linewidth]{figures/model_link_error_proj2_detourr} \caption{Screenshots of the link plots showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\text{-}D$ (right) using `detourr`.}\label{fig:unnamed-chunk-45}
\end{figure}
